Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-24 main_paper.tex
[#22] Update simulation tables with correct bias values
Commit f12975e updated the R code to report the correct bias values
for each estimator in the Monte Carlo simulations. This commit fixes
the tables to report those values. (This was done by manually flipping
the signs, not by rerunning everything.)

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs (with $\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
and~\eqref{eq:15}.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
      & CCT            & --0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\ 
      & Naive          & --0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\ 
    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
      & CCT            & --0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\ 
      & Naive          & --0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\ 
    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
      & CCT            & --0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\ 
      & Naive          &   0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
      & CCT            & --0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\ 
      & Naive          & --0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\ 
    2 & Wild bootstrap & --0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\ 
      & CCT            & --0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\ 
      & Naive          & --0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\ 
    3 & Wild bootstrap & --0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\ 
      & CCT            & --0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\ 
      & Naive          &   0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\  
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

@@

We reestimate the ATE on health and schooling with robust procedures. To be
specific, we apply both the robust procedure proposed by CCT and the bootstrap
procedure introduced in this paper.  Our bootstrap estimator uses the
AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
bootstrap from \citet{DF08}; see Equations~\eqref{eq:14} and~\eqref{eq:15} of
this paper and the surrounding remarks. In the bootstrap
procedure, we use 500 bootstraps for bias correction and 999 to calculate the
confidence intervals. The analytical estimator using CCT's bias correction and
variance estimator uses
their AMSE-optimal bandwidths as well.

>>>>

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs (with $\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
and~\eqref{eq:15}. In these simulations, we use Mammen's (1993) \nocite{Mam93}
two-point distribution for $e_i^*$ in the bootstrap:
\begin{equation}
  \label{eq:19}
  e_i^* =
  \begin{cases}
    \frac{1 + \sqrt{5}}{2} & \text{with probability\ } \frac{\sqrt{5} - 1}{2 \sqrt{5}} \\
    \frac{1 - \sqrt{5}}{2} & \text{otherwise}.
  \end{cases}
\end{equation}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & 0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\
      & CCT            & 0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\
      & Naive          & 0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\
    2 & Wild bootstrap & 0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\
      & CCT            & 0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\
      & Naive          & 0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\
    3 & Wild bootstrap & 0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\
      & CCT            & 0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\
      & Naive          & --0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & 0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
      & CCT            & 0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\
      & Naive          & 0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\
    2 & Wild bootstrap & 0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\
      & CCT            & 0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\
      & Naive          & 0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\
    3 & Wild bootstrap & 0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\
      & CCT            & 0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\
      & Naive          & --0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

@@

We reestimate the ATE on health and schooling with robust procedures. To be
specific, we apply both the robust procedure proposed by CCT and the bootstrap
procedure introduced in this paper.  Our bootstrap estimator uses the
AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
bootstrap from \citet{DF08} with Mammen's (1993) two-point distribution
on $e^*_i$; see Equations~\eqref{eq:14} and~\eqref{eq:15} of
this paper and their surrounding remarks as well as Equation~(\ref{eq:19}) for
formal definitions. In the bootstrap
procedure, we use 500 bootstraps for bias correction and 999 to calculate the
confidence intervals. The analytical estimator using CCT's bias correction and
variance estimator uses
their AMSE-optimal bandwidths as well.
